---
title: "Quarto Example: YML features, Sourced setup"
author: "JY"
date: last-modified
format: 
  html:
    theme: united
    toc: true
    code-fold: true
    number-sections: true
knitr:
  opts_chunk:
    fig-height: 4
    fig-width: 6
execute: 
  echo: true
  warning: false
---

```{r setup, include = FALSE}
# reference file with common setup settings
source('_common.R')
```

Basic Quarto doc with **added features** in yaml header AND:

-   referencing setup options from a **\_common.R** file instead of placing in code chunk, making it easy to set settings in one place for reuse in multiple docs. #win!

## Get Data

### Swiss dataset

```{r get_data}
sw <- datasets::swiss
sw$Prov <- rownames(sw)
sw <- sw %>% select(Prov, c(1:ncol(sw)-1))
```

## Explore

### Summaries

```{r}
str(sw)
# glimpse(sw) # no clear advantage over str
summary(sw)
```

### Correlations & Distribution

```{r correlations}
#| fig-height: 6
#| fig-width: 8
chart.Correlation(sw[,2:7], histogram = TRUE)
```

### In-depth Review

#### skimr

```{r skimr}
skim(sw)
```

#### DataExplorer

Not used - creates a separate, detailed html file that loads in browser

```{r DataExplorer}
# DataExplorer creates separate html doc and loads in browser - detailed exploration of data
#create_report(sw)
```

#### summarytools

```{r summarytools}
dfSummary(sw, plain.ascii = TRUE, style = 'grid', tmp.img.dir = "/tmp")
```

### Boxplot summary

```{r}
# pivot sw to have all metrics in a metrics col and values in a values col
sw_long <- sw %>% pivot_longer(cols = c(2:7), names_to = "metric", values_to = "value")
sw_long %>% ggplot(aes(x=metric, y=value))+geom_boxplot()
```
