---
title: "Quarto Template: Basic EDA"
author: "JY"
date: last-modified
format: 
  html:
    theme: united
    toc: true
    code-fold: true
    number-sections: true
knitr:
  opts_chunk:
    fig-height: 4
    fig-width: 6
execute: 
  echo: true
  warning: false
---

```{r setup, include = FALSE}
# reference file with common setup settings
source('_common.R')
```

## Intro

\[a template for basic exploratory data analysis. use to get started and edit as necessary for purposes.\]

::: callout-note
\[Requires \_common.R file in same directory (or change source command)\]
:::

### Usage

Source file is maintained in github repo at [github.com/jyuill/quarto-templates/basic-eda](https://github.com/jyuill/quarto-templates/tree/714824c70e4e29e329922f9e3a58815bbd0b1f03/basic-eda).

To use in Quarto project, simply:

1.  Terminal: **quarto use template jyuill/quarto-templates/basic-eda**
2.  Automatically checks for github repo and copies files in directory
3.  Will prompt for folder name \> renames the original template.qmd file with folder name
4.  Edit and develop as needed, based on example content here

## Get Data

### \[EUStockMarkets\]

\[built-in dataset EuStockMarkets to serve as example\]

```{r get_data}
data <- as.data.frame(datasets::EuStockMarkets) # time series convert to df
data$date <- seq.Date(from=as.Date('1990-01-02'), by=1, length.out = nrow(data))
data <- data %>% select(date, c(1:ncol(data)-1))
```

## Explore

### Summaries

```{r}
str(data)
summary(data)
```

### Correlations & Distribution

```{r correlations}
#| fig-height: 6
#| fig-width: 8
chart.Correlation(data[,2:ncol(data)], histogram = TRUE)
```

### In-depth Review

#### skimr

```{r skimr}
skim(data)
```

### Boxplot summary

```{r}
# pivot sw to have all metrics in a metrics col and values in a values col
data_long <- data %>% pivot_longer(cols = c(2:ncol(data)), names_to = "mkt", values_to = "price")
data_long %>% ggplot(aes(x=price, y=mkt))+geom_boxplot()
```

### Trend

```{r}
data_long %>% ggplot(aes(x=date, y=price, color=mkt))+geom_line()
```
