---
title: "Quarto Template"
author: "JY"
date: last-modified
format: 
  html:
    theme: united
    toc: true
    code-fold: true
    number-sections: true
knitr:
  opts_chunk:
    fig-height: 4
    fig-width: 6
execute: 
  echo: true
  warning: false
---

```{r setup, include = FALSE}
# reference file with common setup settings
source('_common_ext.R')
```

## Intro

-   this doc is created based on a the **template.qmd file + \_*common*\_ext.R** file from \_***extension*****\_01** folder. used as a starter template to be edited/built upon.
-   created by running this in terminal:
    -   <div>

        > quarto use template \_*extensions*\_01

        </div>
-   this prompts you to specify the directory name, copies over the files in extensions_01, and renames template.qmd to name of directory.

::: callout-note
Can also run template from github repo: see template in template_test_github_01 folder.
:::

## Get Data

### \[EUStockMarkets\]

\[built-in dataset EuStockMarkets to serve as example\]

```{r get_data}
data <- as.data.frame(datasets::EuStockMarkets) # time series convert to df
data$date <- seq.Date(from=as.Date('1990-01-02'), by=1, length.out = nrow(data))
data <- data %>% select(date, c(1:ncol(data)-1))
```

## Explore

### Summaries

```{r}
str(data)
summary(data)
```

### Correlations & Distribution

```{r correlations}
#| fig-height: 6
#| fig-width: 8
chart.Correlation(data[,2:ncol(data)], histogram = TRUE)
```

### In-depth Review

#### skimr

```{r skimr}
skim(data)
```

### Boxplot summary

```{r}
# pivot sw to have all metrics in a metrics col and values in a values col
data_long <- data %>% pivot_longer(cols = c(2:ncol(data)), names_to = "mkt", values_to = "price")
data_long %>% ggplot(aes(x=price, y=mkt))+geom_boxplot()
```

### Trend

```{r}
data_long %>% ggplot(aes(x=date, y=price, color=mkt))+geom_line()
```
